Methods for Large Scale Learning to Rank

### 2014-04-09 report/Chapters/CrossBenchmarkComparison.tex
baseline annotaties

\section{Evaluation Results Found in Literature}
Table~\ref{tab:ltr_methods_used} gives an overview of the Learning-to-Rank methods for which evaluation results were found for one of the benchmark datasets listed in section~\ref{sec:collecting_evaluation_results} through the literature review process also described in section~\ref{sec:collecting_evaluation_results}.\\

@@

\scalebox{0.80}{

@@

AdaRank-\acs{MAP} & \cite{Xu2007} &  & Linear Regression & \cite{Cossock2006} & \cite{Wang2012, Volkovs2011} \\ 
AdaRank-\acs{nDCG} & \cite{Xu2007} & \cite{Busa-Fekete2013,Tan2013} & List\acs{MLE} & \cite{Xia2008} & \cite{Lin2010, Lin2011, Gao2014} \\ 
ADMM & \cite{Duh2011} & \cite{Duh2011} & ListNet & \cite{Cao2007} &  \\ 

@@

Best Single Feature &  & \cite{Gomes2013} & MHR & \cite{Qin2007} &  \\ 

@@

DCMP & \cite{Renjifo2012}  & \cite{Renjifo2012}  & RankBoost & \cite{Freund2003} & \cite{Busa-Fekete2013, Alcantara2010} \\ 

@@

FP-Rank & \cite{Song2013} & \cite{Song2013} & Rank\acs{SVM} & \cite{Herbrich1999, Joachims2002} & \cite{Busa-Fekete2013, Freno2011, He2010, Alcantara2010} \\ 
FRank & \cite{Tsai2007} & \cite{Wang2012} & Rank\acs{SVM}-Primal &  & \cite{Lai2011} \\ 
FSMRank & \cite{Lai2013c} & \cite{Lai2013c,Laporte2013} & Rank\acs{SVM}-Struct &  &  \\

@@

\acs{GP}Rank & \cite{Silva2009} & \cite{Torkestani2012} & Ridge Regression & \cite{Cossock2006} &  \\

@@

Group\acs{MLE} & \cite{Lin2010} & \cite{Lin2011} & SmoothRank & \cite{Chapelle2010} & \cite{Chapelle2010} \\

@@

KL-\acs{CRF} & \cite{Volkovs2011} & \cite{Volkovs2011} & \acs{SVM}$^{\acs{MAP}}$ & \cite{Yue2007} & \cite{Wang2012, Xu2008, Niu2012} \\ 

>>>>

\section{Evaluation Results Found in Literature}
Table \ref{tab:ltr_methods_used} gives an overview of the Learning-to-Rank methods for which evaluation results were found for one of the benchmark datasets listed in section~\ref{sec:collecting_evaluation_results} through the literature review process also described in section~\ref{sec:collecting_evaluation_results}. Occurrences of L2, L3 and L4 in Table \ref{tab:ltr_methods_used} imply that these algorithms are evaluated as official LETOR 2.0, LETOR 3.0 and LETOR 4.0 baselines respectively.\\

@@

\scalebox{0.75}{

@@

AdaRank-\acs{MAP} & \cite{Xu2007} & L2, L3, L4 & Linear Regression & \cite{Cossock2006} & L3, \cite{Wang2012, Volkovs2011} \\ 
AdaRank-\acs{nDCG} & \cite{Xu2007} & L2, L3, L4,  \cite{Busa-Fekete2013,Tan2013} & List\acs{MLE} & \cite{Xia2008} & \cite{Lin2010, Lin2011, Gao2014} \\ 
ADMM & \cite{Duh2011} & \cite{Duh2011} & ListNet & \cite{Cao2007} & L2, L3, L4 \\ 

@@

Best Single Feature &  & \cite{Gomes2013} & MHR & L2, \cite{Qin2007} &  \\ 

@@

DCMP & \cite{Renjifo2012}  & \cite{Renjifo2012}  & RankBoost & \cite{Freund2003} & L2, L3, L4, \cite{Busa-Fekete2013, Alcantara2010} \\ 

@@

FP-Rank & \cite{Song2013} & \cite{Song2013} & Rank\acs{SVM} & \cite{Herbrich1999, Joachims2002} & L2, L3, \cite{Busa-Fekete2013, Freno2011, He2010, Alcantara2010} \\ 
FRank & \cite{Tsai2007} & L2, L3, \cite{Wang2012} & Rank\acs{SVM}-Primal &  & L3, \cite{Lai2011} \\ 
FSMRank & \cite{Lai2013c} & \cite{Lai2013c,Laporte2013} & Rank\acs{SVM}-Struct &  & L3, L4 \\

@@

\acs{GP}Rank & \cite{Silva2009} & \cite{Torkestani2012} & Ridge Regression & \cite{Cossock2006} & L3 \\

@@

Group\acs{MLE} & \cite{Lin2010} & \cite{Lin2011} & SmoothRank & \cite{Chapelle2010} & L3, \cite{Chapelle2010} \\

@@

KL-\acs{CRF} & \cite{Volkovs2011} & \cite{Volkovs2011} & \acs{SVM}$^{\acs{MAP}}$ & \cite{Yue2007} & L3, \cite{Wang2012, Xu2008, Niu2012} \\ 
